EpisoDAS - DAS-based Password Generation \\ using Episodic Memories

### 2018-01-21 paper/AVI2018/paper.tex
投稿版 (たぶん)

We propose a new visual password generation system \textit{EpisoDAS}
that posesses the advantages of both EpisoPass and DAS-based methods.

@@

The contents and the order of the questions
do not depend on the user's actions, and
the user cannot tell whether he has selected a right answer.
%
After repeating the slection process ten times,
the user can get his password
calculated from his selections (Figure \ref{Result}).

@@

Users can select correct answers not only by clicking each button,
but by draggin the pointing device on the buttons.
%
If the series of button locations form a special pattern,
% If the series of buttons are aligned next to each others,
the user can drag the pointing device like
Figure \ref{draw} instead of clicking ten buttons,
and quickly generate a password.
%
The order of the list of candidate answers change according to the
drag or click action,
and the user can mix the dragging and clicking actions at any point.
The user can either click ``Boston'' and ``Los Angeles'' one by one or
click on ``Boston'' and drag the pointing device downward to select
``Los Angeles'' without releasing the mouse button or releasing the
pen or finger from the surface of the tablet computer.

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1356 1046]{figures/draw.png}
  \caption{Drawing a secret pattern on EpisoDAS.}
  \label{draw}
\end{figure}

@@

EpisoDAS can be used for generating passwords for any kind of systems and
services, but it is most useful when it is used to log into a Web service.
Figure \ref{Amazon} shows how a user can use EpisoDAS when
he wants to log in to Amazon.com.
If the EpisoDAS extension is installed on the browser,
an EpisoDAS window appears when a user enters their
email address and clicks the password field.
After selecting answers by drawing a secret pattern on the EpisoDAS area,
a password for Amazon is generated and pasted
into the password field, making the user to log in without typing a password.

@@

The data used in the above example is retrieved from the EpisoDAS database
on the Web, using the name of the service (\texttt{Amazon})
and the user id (\texttt{john@example.com}).

@@

After selecting the correct answers
(``Boston'', ``Los Angeles'', etc.) on the EpisoPass editor page (Figure \ref{EpisoPass}),
the user can click the ``DAS'' button on the top-right portion of the
page to proceed to specify their DAS patten.

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1332 1118]{figures/DASRegister.png}
  \caption{Registring the DAS pattern}
  \label{DASRegister}
\end{figure}

If the user wants to use a U-shape as the secret pattern,
he can draw the shape shown in Figure \ref{DASRegister}
on the DAS registration window.
%
After registering the pattern, the candidate answers for the EpisoPass is
shuffled so that the series of correct answers represent the specified pattern.

@@

Questions and answer candidates can be edited interactively on the
EpisoPass editor page (Figure \ref{EpisoPass}) and arbitrary
strings can be specified as questions and answer candidates.
However, creating many questions and answer candidates is
time-consuming and hard task, because
people usually feel it difficult to recall old secret episodes.
%
To help people easily create EpisoPass questions and answers,
a support page can be used for easy problem creation
(Figure \ref{Easy}).

\begin{figure}[H]
  \includegraphics[width=12cm,bb=0 0 1678 1728]{figures/Easy.png}
  \caption{Easily creating questions and answers}
  \label{Easy}
\end{figure}

@@

Recalling special old episodes is sounds hard for many people, but
recalling an attribute of an old friends is much easier.
The questions and answers shown in Figure \ref{EpisoPass} was
created by this system,
using place names instead of people's names.

@@

The authors have been using EpisoPass for more than 5 years, and
using EpisoDAS for about an year.
No formal evaluation has been performed so far, but
some people around the authors are enthusiastically using
EpisoDAS for their daily work, and
important impressions have been observed during the period.

@@

The biggest advantage of using EpisoPass is that users don't have to
remember long password strings.
%
After the authors began using EpisoPass,
they have been having no problem forgetting passwords of any kind.
%
As long as a user have the seed string and question-answer data,
he can easily generate passwords by running
EpisoPass and answering the questions.
%
If the questions are based on old unforgettable episodic memory,
there is little chance of losing the password for a service
as long as the seed string and questions are available.
%
If the user's memory is related to an episode that took place 20 years
ago, say, and the user clearly still remembers the episode now, it is
unlikely the episode will be forgotten in the future.

@@

EpisoDAS is implemented as a single HTML file that includes a JavaScript
script for password calculation.
The HTML file can be put on the Web or saved in a handy USB memory device
so that it can be accessed from a Web browser.
%
If the questions are based on the user's secret memories and
a sufficient number of questions and fake answers are provided,
the data can be put on a public Web page or saved in a secure
repository like GitHub.
%
The data set of the authors are put on the Web, and it can be easily
found using Web search engines\footnote{
  The EpisoDAS data of the authors can be found on major Web
  search enginges using the name of the author and ``password''.
}.
It means that the passwords used by the authors can be retrieved
even when the data is not available locally.

@@

Using EpisoDAS, people can use password-based systems
only by selecting answers based on their episodic memories,
without remembering passwords or using password management systems.
Using a browser extension,
people can use services without noticing that passwords are
required for the service.

Creating a Q-A database is a one-time process,
after which the system becomes straightforward to use.
%
With a proper help, creating a database is not difficult even for
people who are not good at using computers.
A helper can ask the client questions like
``Do you remember an interesting friend in your childfood?''
to get the list of old friends, and then ask questions like
``What kind of child was he?'', ``Do you remember his house?''
to create a question for locating him.
With such information, the helper can use the technique shwon
in Section \ref{easyregister} to create the EpisoDAS database
for the client.

@@

The strength of the generated passwords depends on the number and 
level of secrecy of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326,Komanduri:2011:PPM:1978942.1979321}, % What password is strong
but measuring the strength of secret questions is an area where more study is needed.
% \marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is
% considerably more than a billion (closer to 10 thousand billion,
% (US) or 10 million million (UK).}
Using ten secret questions each with twenty answers, where each answer is considered equally likely,
an attacker would need to cover a search space of over ten trillion ($20^{10}$) values to check
every potential combination of answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
This represents roughly the same entropy as using a random 8-character Latin-alphabet
password, for which the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where it's not possible to perform online brute-force attacks \cite{Florencio:2007:SWP:1361419.1361429}.

@@

The quality of the questions is key to using EpisoDAS effectively.  If
the episode is shared by someone else, this other person might easily
be able to answer the question and generate the user's password.
%
The episode related to each question should therefore not be known to any other person,
and the episode should be unforgettable.
%
Finding such episodes seems difficult at first,
but using the method shown in the last section,
it is not extremely difficult to recall
many trivial episodes which are unforgettable but
nonetheless not important to other people.

@@

\subsection{Developmenet of browser extensions}

EpisoDAS browser extension is very useful, but creating the extension
is cumbersome because there is no standard login form for
Web services.
%
The browser extension should first detect that the Web page is a login page
of a Web service (e.g. Amazon),
and then it should be able to get the ID of the user
and know where the result of EpisoDAS calculation should be pasted.
%
Commercial password managers\cite{OnePassword,Dashlane,LastPass,KeyPass,NortonIDSafe,IDManager}
are usually well integrated with Web browsers,
and EpisoDAS should also be evolved so that
the browser extension works on many Web services.

\subsection{Battles against sholder surfing}

@@

This problem is common to all the DAS-based authentication systems,
and great care should be taken when drawing a secret in the public.
EpisoDAS users can use more complex DAS patterns than
conventional DAS systems,
because there is no risk of forgetting the pattern,
since the user can read the question at any time and
remember the secret pattern which corresponds to the
answers to the questions.

\subsection{Risks of Forgetting DAS pattern}

Using a conventional DAS system, users should be carefull about
remembering the DAS pattern.
DAS patterns may be more easily remembered than password texts,
but there is always some risks about forgetting them.
Using EpisoDAS, users can easily remember the DAS pattern
just by reading the questions and answers.
Users can be very sure that they will never forget the pattern,
because the pattern can be retrieved by answering the questions.

EpisoDAS is the combination of EpisoPass and DAS-based authentication methods.
A user can generate a password using his episodic memories, or
he can generate a password using the DAS pattern he remembers.

@@

We introduced a password management system \textit{EpisoDAS}
that generates a password from a seed string by
quicly drawingn a secret pattern backed by the user's episodic memories.
These memories are represented as a set of questions and answers
which can be solved only by the user in order to generate a site-specific password.
%
Using EpisoDAS, a user can log into Web services quickly without
worrying about
having to remember any secret information, other than the episodic memories
that have been chosen specifically to be easy to recall.
%
We are hoping to make EpisoDAS available on all the environments
where strong passwords are required, and
relieve everyone's pain of password handling.

>>>>

We propose a new visual password generation system \textit{EpisoDAS}
that possesses the advantages of both EpisoPass and DAS-based methods.

@@

The contents and the order of the questions
do not depend on the user's actions, and
the user cannot tell whether he has selected a right answer.
%
After repeating the selection process ten times,
the user can get his password
calculated from his selections (Figure \ref{Result}).

@@

Users can select correct answers not only by clicking each button,
but by dragging the pointing device on the buttons.
%
If the series of button locations form a special pattern,
% If the series of buttons are aligned next to each others,
the user can drag the pointing device like
Figure \ref{draw} instead of clicking ten buttons,
and quickly generate a password.
%
The order of the list of candidate answers changes according to the
drag or click action,
and the user can mix the dragging and clicking actions at any point.
The user can either click ``Boston'' and ``Los Angeles'' one by one or
click on ``Boston'' and drag the pointing device downward to select
``Los Angeles'' without releasing the mouse button or releasing the
pen or finger from the surface of the tablet computer.

\begin{figure}[H]
  \includegraphics[width=10cm,bb=-60 0 1296 1046]{figures/draw.png}
  \caption{Drawing a secret pattern on EpisoDAS.}
  \label{draw}
\end{figure}

@@

EpisoDAS can be used for generating passwords for any kind of systems and
services, but it is most useful when it is used to log into a Web service.
Figure \ref{Amazon} shows how a user can use EpisoDAS when
he wants to log into Amazon.com.
If the EpisoDAS extension is installed on the browser,
an EpisoDAS window appears when a user enters their
email address and clicks the password field.
After selecting answers by drawing a secret pattern on the EpisoDAS area,
a password for Amazon is generated and pasted
into the password field, making the user to log in without typing a password.

@@

The data used in the above example is retrieved from the EpisoDAS database
created and saved on the EpisoPass page (Figure \ref{EpisoPass}),
with the name of the service (\texttt{Amazon})
and the user id (\texttt{john@example.com}).

@@

After selecting the correct answers
(``Boston'', ``Los Angeles'', etc.) on the EpisoPass editor page (Figure \ref{EpisoPass}),
the user can click the ``DAS'' button on the top-right portion of the
page to proceed to specify their DAS pattern.

\begin{figure}[H]
  \includegraphics[width=10cm,bb=-60 0 1272 1118]{figures/DASRegister.png}
  \caption{Registering the DAS pattern}
  \label{DASRegister}
\end{figure}

If the user wants to use a U-shape as the secret pattern,
he can draw the shape shown in Figure \ref{DASRegister}
on the DAS registration window.
%
After registering the pattern, the candidate answers for the EpisoPass is
shuffled so that the series of correct answers represent the
specified pattern (U-shape in this case).

@@

Questions and answer candidates can be edited interactively on the
EpisoPass editor page (Figure \ref{EpisoPass}) and arbitrary
strings can be specified as questions and answer candidates.
However, creating many questions and answer candidates is
time-consuming and hard, because
people usually feel it difficult to recall old secret episodes.
%
To help people easily create EpisoPass questions and answers,
a support page can be used for creating problems easily
(Figure \ref{Easy}).

\begin{figure}[t]
  \includegraphics[width=12cm,bb=0 0 1522 1632]{figures/Easy.png}
  \caption{A Q-A creation helper.}
  \label{Easy}
\end{figure}

@@

Recalling special old episodes sounds hard for many people, but
recalling an attribute of an old friends is much easier.
The questions and answers shown in Figure \ref{EpisoPass} was
created by this system,
using place names instead of people's names.

@@

The authors have been using EpisoPass for more than 5 years, and
using EpisoDAS for about an year.
No formal evaluation has been performed so far, but
some people around the authors are enthusiastically using
EpisoDAS for their daily activities, and
important impressions have been observed during the period.

@@

The biggest advantage of using EpisoPass and EpisoDAS is that users don't have to
remember long password strings.
%
After the authors began using EpisoPass,
they have been having no problem forgetting passwords of any kind.
%
As long as a user have the seed string and question-answer data,
they can easily generate passwords by running
EpisoPass and answering the questions.
%
If the questions are based on old unforgettable episodic memories,
there is little chance of losing the password for a service
as long as the seed string and questions are available.
%
If the user's memory is related to an episode that took place 20 years
ago, say, and the user clearly still remembers the episode now, it is
unlikely the episode will be forgotten in the future.

@@

EpisoDAS is implemented as a single HTML file that includes a JavaScript
code for password calculation.
The HTML file can be put on the Web or saved in a handy memory device
so that it can be accessed from any Web browser easily.
%
If the questions are based on the user's secret memories and
a sufficient number of questions and fake answers are provided,
the data can be put on a public Web page or saved in a secure
repository like GitHub.
%
The data set of the authors are put on the Web, and it can be easily
found using Web search engines\footnote{
  The EpisoDAS data of the authors can be found on major Web
  search engines using the name of the author and
  the keyword ``\texttt{password}''.
}.
It means that the passwords used by the authors can be retrieved
even when the data is not available locally.

@@

Using EpisoDAS, people can use password-based systems
only by selecting answers based on their episodic memories,
without remembering passwords or using password management systems.
Using a browser extension,
people can use Web services without noticing that passwords are
required for the service.

Creating a Q-A database is a one-time process,
after which the system becomes straightforward to use.
%
With a proper help, creating a database is not difficult even for
people who are not good at using computers.
A helper can ask the client questions like
``Do you remember your friends in your childhood?''
to get the list of old friends, and then ask questions like
``What kind of person was this guy?'', ``Do you remember his house?''
to create a question for locating a person.
With such information, the helper can use the support page shown
in Section \ref{easyregister} to create the EpisoDAS database
for the client.

@@

The strength of the generated passwords depends on the number and 
level of secrecy of the questions.
%
There have been many studies on the strength of passwords
\cite{Hayashi:2011:DSP:1978942.1979326}\cite{Komanduri:2011:PPM:1978942.1979321}, % What password is strong
but measuring the strength of secret questions is an area where more study is needed.
% \marginnote{I calculate $20^{10} = 10,240,000,000,000$. This is
% considerably more than a billion (closer to 10 thousand billion,
% (US) or 10 million million (UK).}
Using ten secret questions each with twenty answers, where each answer is considered equally likely,
an attacker would need to cover a search space of over ten trillion ($20^{10}$) values to check
every potential combination of answers,
and the entropy of the system is 43.2 ($10 \times \log_2 20$) bits.  % 10.0 * (Math.log(20.0)/Math.log(2.0))
%
This represents roughly the same entropy as using a random 8-character Latin-alphabet
password, for which the entropy is 45.6 bits.
This level is considered to be strong enough for Web services,
where it's not possible to perform online brute-force attacks \cite{Florencio:2007:SWP:1361419.1361429}.

@@

The quality of the questions is key to using EpisoDAS effectively.  If
the episode is shared by someone else, this other person might easily
be able to answer the question and generate the user's password.
%
The episode related to each question should therefore not be known to any other person,
and the episode should be unforgettable.
%
Finding such episodes seems difficult at first,
but using the method shown in Section \ref{easyregister},
it is not extremely difficult to recall
many trivial episodes which are unforgettable but
nonetheless not important to other people.

@@

\subsection{Development of browser extensions}

EpisoDAS browser extension is very useful, but creating the extension
is cumbersome because there is no standard login form for
Web services.
%
The browser extension should first detect that the Web page is a login page
of a Web service (e.g. Amazon),
and then it should be able to get the ID of the user
and know where the result of EpisoDAS calculation should be pasted.
%
Commercial password managers\cite{OnePassword}\cite{Dashlane}\cite{LastPass}\cite{KeyPass}\cite{NortonIDSafe}\cite{IDManager}
are usually well integrated with Web browsers,
and EpisoDAS should also be evolved so that
the browser extension works on many Web services.

\subsection{Caution about shoulder surfing}

@@

This problem is common to all the DAS-based authentication systems,
and great care should be taken when drawing a secret pattern in the public.
EpisoDAS users can use more complex DAS patterns than
conventional DAS systems,
because there is no risk of forgetting the pattern,
since the user can read the question at any time and
recall the secret pattern which corresponds to the
answers to the questions.

\subsection{Risks of forgetting DAS patterns}

Using a conventional DAS system, users should be careful about
remembering the DAS pattern.
DAS patterns may be more easily remembered than password texts,
but there is always some risks about forgetting them.
Using EpisoDAS, users can easily recall the DAS pattern
just by reading the questions and answers.
Users can be very sure that they will never forget the pattern,
because the pattern can easily be retrieved by answering the questions.

% EpisoDAS is the combination of EpisoPass and DAS-based authentication methods.
% A user can generate a password using his episodic memories, or
% he can generate a password using the DAS pattern he remembers.

@@

We introduced a password management system \textit{EpisoDAS}
that generates a password from a seed string by
quickly drawing a secret pattern backed by the user's episodic memories.
These memories are represented as a set of questions and answers
that can be solved only by the user in order to generate a site-specific password.
%
Using EpisoDAS, a user can log into Web services quickly without
worrying about
having to remember any secret information, other than the episodic memories
that have been chosen specifically to be easy to recall.
%
We are hoping to make EpisoDAS available on all the environments
where strong passwords are required, and
relieve everyone's pain of password handling.
